### 2014-03-17 docs/paper/paper.tex

% FIXME citation about why 2D is ``good enough''
As only one-dimensional and two-dimensional population units have been implemented, networks that require populations to compute functions
of three or more independent variables cannot be simulated with this design.

>>>>

% FIXME citation about why 2D is ``good enough''
As only one-dimensional and two-dimensional population units have been implemented, networks that require populations to compute functions
of three or more independent variables cannot be simulated with this design.
However, the majority of existing models in Nengo do not use populations with more than two input dimensions, so with the exception of
certain very large or very complex models that require representation of high-dimensional quantities, providing only one- and two-dimensional
populations is not expected to be overly restrictive.
